### 2021-08-13 paper/paper.tex
Avoid potential confusion of "this one" referring to reference [45]
Refer to Sec 4.2.2

The package manager \lstinline{Pkg} makes it easy to reproduce the exact runtime environment, including
binary dependencies, used to generate numerical results. We have used this feature for all of our papers based on
\trixi \cite{schlottkelakemper2021purely, ranocha2021preventing}, including this
one \cite{ranocha2021adaptiveRepro}.
This facilitates code sharing and reproducible research in computational science,
which is arguably important but not yet mainstream \cite{barnes2010publish,
donoho2010invitation, leveque2013top}.

@@

Similarly, there is no need to compile HDF5 on a user system due to the
availability of HDF5.jl\footnote{\url{https://github.com/JuliaIO/HDF5.jl}}.
There is still work to be done how to improve the experience in combination
with MPI on HPC clusters, but some promising
approaches exist \cite{byrne2021mpi}.

@@

\subsubsection{Simulations with distributed-memory parallelism}

>>>>

The package manager \lstinline{Pkg} makes it easy to reproduce the exact runtime environment, including
binary dependencies, used to generate numerical results. We have used this feature for all of our papers based on
\trixi \cite{schlottkelakemper2021purely, ranocha2021preventing}, including the present manuscript
\cite{ranocha2021adaptiveRepro}.
This facilitates code sharing and reproducible research in computational science,
which is arguably important but not yet mainstream \cite{barnes2010publish,
donoho2010invitation, leveque2013top}.

@@

Similarly, there is no need to compile HDF5 on a user system due to the
availability of HDF5.jl\footnote{\url{https://github.com/JuliaIO/HDF5.jl}}.
There is still work to be done on how to improve the experience in combination
with MPI on HPC clusters, but some promising
approaches exist (see Section~\ref{sec:distributed-memory}).

@@

\subsubsection{Simulations with distributed-memory parallelism}
\label{sec:distributed-memory}
